How fluid-mechanical erosion creates anisotropic porous media

### 2022-06-29 docs/PhysicsPaper/StokesErosion.tex
N<

Similar statistical analysis is performed on the tortuosity measurements and shown in Figure~\ref{fig6}(a)--(b). In all simulations, the longitudinal tortuosity decreases with time as erosion allows passive tracers to take more direct paths when traveling in the flow direction. In contrast, Fig.~\ref{fig6}(b) shows the transverse tortuosity can increase with time, as passive tracers must work to circumvent horizontally aligned bodies when traveling in the vertical direction.
Measurements of the tortuosity ratio, $(T_2 -1)/(T_1 -1)$ show similar behavior across different values of $M$, as seen in Figure~\ref{fig6}(c). For nearly all runs, the tortuosity ratio increases as bodies erode, and maximum ratio of roughly $(T_2 -1)/(T_1 -1) = 8$ is reached. Finally, the tortuosity ratio decreases near the very end of the simulation. As before the tortuosity ratio can be decomposed into configurational and shape components, as shown in Figures~\ref{fig6}(d)--(e). The shape component is the main contribution, and the configurational component of the tortuosity ratio is minimal.

>>>>

Similar statistical analysis is performed on the tortuosity measurements and shown in Figure~\ref{fig6}(a)--(b). In all simulations, the longitudinal tortuosity decreases with time as erosion allows passive tracers to take more direct paths when traveling in the flow direction. In contrast, Fig.~\ref{fig6}(b) shows the transverse tortuosity can increase with time, as vertically-traveling passive tracers must work to circumvent horizontally aligned bodies carved by erosion.

The tortuosity ratio, $(T_2 -1)/(T_1 -1)$, provides a second proxy for medium anisotropy to complement the permeability measurements. Figure~\ref{fig6}(c) shows that the tortuosity ratio behaves similarly across different values of $M$. The ratio increases substantially with erosion, reaching a peak of roughly $(T_2 -1)/(T_1 -1) = 8$, before descending during the final stages of erosion. As before the tortuosity ratio can be decomposed into configurational and shape components, as shown in Figures~\ref{fig6}(d)--(e). Here, we see that the shape component is the main contribution, and the configurational component of the tortuosity ratio is minimal. This observation fits with the intuition that the main hindrance to a passive tracer should be the shape of individual obstructions, rather than how those obstructions are arranged relative to one another. As such, the tortuosity ratio is a less sensitive indicator of channelization than is the permeability ratio.
